### 2021-08-27 manuscript.Rmd
U[dates

```{r CFA, }
LB.cfa <- read_excel("Processed Data/SpitschanSleepSurvey_DATA_2021-08-24_1819_redacted_199_CFA.xlsx")
LB.cfa$id <- NULL
summarize <- summary(LB.cfa)
Descriptives <- psych::describe(LB.cfa)
#Univariate Normality
normality <- normality(LB.cfa) 
#Multivariate Normality
mardia(LB.cfa, na.rm = T, plot =F)

>>>>

```{r CFA, }
LB.cfa <- read_excel("SpitschanSleepSurvey_DATA_2021-08-24_1819_redacted_199_CFA.xlsx")
LB.cfa$id <- NULL
summarize <- summary(LB.cfa)
Descriptives <- psych::describe(LB.cfa)
#Univariate Normality
normality <- normality(LB.cfa) 
#Multivariate Normality
mardia(LB.cfa, na.rm = T, plot =F)
